Self Regulation Ontology Retest Data Report

### 2018-01-19 code/SRO_Report.Rmd
updating report for draft

tmp %>%
  group_by(overall_difference, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

>>>>

tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(overall_difference, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```
